quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2024-06-23 paper-quollr.Rmd
Add 2D vis functions
Add 2D vis description

<!--add each step separately-->

@@

@@

>>>>

<!--add each step separately-->
<!--add hexbin notation image-->

@@

The `geom_hexgrid()` function is used to plot the hexagonal grid from the provided centroid data set.

```{r, echo=TRUE, eval=FALSE}
ggplot() + 
  geom_hexgrid(
    data = all_centroids_df, 
    aes(x = c_x, y = c_y)
    ) +
  coord_fixed()
```

To visualize the $2\text{-}D$ model, mainly three functions are used. As shown in Figure \@ref(fig:mesh-plots)a, `geom_trimesh()` to visualize the triangular mesh by adding a new layer to `ggplot()`. After identifying benchmark value to remove long edge, `vis_lg_mesh()` is used to visualize the triangular mesh by coloring the small and long edges. As shown in Figure \@ref(fig:mesh-plots)b, the small and long edges are colored by black and red respectively. Following this, `vis_rmlg_mesh()` is used to visualize smoothed $2\text{-}D$ model which is the $2\text{-}D$ model after removing the long edges (see Figure \@ref(fig:mesh-plots)c). In `vis_lg_mesh()` and `vis_rmlg_mesh()`, `benchmark_value` argument controls the edge removal in $2\text{-}D$. Using small value of `benchmark_value`, will produce a triangular mesh with missing data structure; for example `benchmark_value = 0.3` shows two clusters rather than continuous structure, while `benchmark_value = 0.8` creates long edges and mislead the data structure in $p\text{-}D$ space.

```{r, echo=TRUE, eval=FALSE}
ggplot() + 
  geom_trimesh(
    data = df_bin_centroids, 
    aes(x = c_x, y = c_y)
    ) +
  coord_fixed()
```

@@

Displaying the $p\text{-}D$ model overlaid on the data is done using the function `show_langevitour()`. This visualization is helpful for visually evaluating how well the model fits the data. The function requires several arguments: data along with their corresponding hexagonal bin ID, $2\text{-}D$ and $p\text{-}D$ model points, the threshold for removing long edges, and the distance data set.
